Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-09 figures/masked_filters.tex
add figure for masking

\begin{figure*}[htb]
	% blog post on how to use pgf from matplotlib to latex
	% https://timodenk.com/blog/exporting-matplotlib-plots-to-latex/
	% \usepackage{layouts} and \printinunitsof{cm}\prntlen{\textwidth} show that textwidth is 17cm here.
	\centering
	\input{figures/first_layer.pgf}
	\vspace{-0.25cm}
	\caption{Frequency responses for (parts of) the different \fes. (a)-(d) show the frequency response of the filters in the first layer that operates on the waveform. (e)-(f) show the frequency response of the complete learned \fe.}
	\label{fig:first_layer}
\end{figure*}

>>>>

\begin{figure}[htb]
	% blog post on how to use pgf from matplotlib to latex
	% https://timodenk.com/blog/exporting-matplotlib-plots-to-latex/
	% \usepackage{layouts} and \printinunitsof{cm}\prntlen{\textwidth} show that textwidth is 17cm here.
	\centering
	\input{figures/masked_filters.pgf}
	\vspace{-0.3cm}
	\caption{\gls{WER} [\%] on \devother using the \gls{SC} features, where $N$ filters of the first layer are masked out based on the peak-to-average value of their frequency response.}
	\label{fig:masked_filters}
\end{figure}

### 2023-03-09 main.tex
add figure for masking

\subsection{Filter Masking}
The observed uncharacteristic wideband filters from \refSec{sec:freq_resp} raise the question whether their output is particularly helpful for the model in addition to the bandpass filters or if they are just not trained properly and ignored by the system.
To answer this question, we masked a portion of the 150 filters in the \gls{SC} features' first layer.
The filters are sorted by the peak-to-average ratio of their frequency response and the $N$ filters with the lowest ratio are masked out and replaced by zeros.
\TODO{Show results}.
We can observe that masking the first 20 filters has no effect on the \gls{WER} and only after masking a 50, so a third of all filters, the \gls{WER} degrades significantly.
This demonstrates that the wideband filters do not contain valuable information for the \gls{ASR} system and are rather the result of a suboptimal training process.
Future work should address this observation to allow a better exploitation of the \fe's potential.

>>>>

\subsection{Filter Masking}
\input{figures/masked_filters}
The observed uncharacteristic wideband filters from \refSec{sec:freq_resp} raise the question whether their output is particularly helpful for the model in addition to the bandpass filters or if they are just not trained properly and ignored by the system.
To answer this question, we masked a portion of the 150 filters in the \gls{SC} features' first layer.
The filters are sorted by the peak-to-average ratio of their frequency response and the $N$ filters with the lowest ratio are masked out and replaced by zeros.
In \refFig{fig:masked_filters}, we can observe that masking the first 20 filters has no effect on the \gls{WER} and only after masking a 50, so a third of all filters, the \gls{WER} degrades significantly.
This demonstrates that the wideband filters do not contain valuable information for the \gls{ASR} system and are rather the result of a suboptimal training process.
Future work should address this observation to allow a better exploitation of the \fe's potential.
